\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-08-21 notes/2loopNLSM.tex
Starting to add commentary to points.

\subsection{Color-dual Bootstrap}
Some background here on how we approach color-dual bootstrap (as we will utilize in our two-loop construction). Building an ansatz from irreducible lorentz products (ISPs). Comments about:
\begin{itemize}
\item loop momenta weight counting 
\item polynomial vector spaces 
\item generalized gauge freedom
\item functional jacobi constraints and cuts
\end{itemize}

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
assumptions for integrand numerators (ordered accoring to the
reference):
\begin{enumerate}
\item Locality: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
\item Power-counting: The maximum power of the loop momenta in the
  numerator is bounded by Feynman-gauge Feynman rules.
\item Cubic diagrams: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item Relabeling : The diagram numerators are only a function of the
  diagram's topology and labeling.
\item Symmetries: The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}.
\item Unitarity cuts: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\item Color-kinematics duality: The numerators obey some form of the
  kinematic Jacobi relations.
\end{enumerate}

@@

\subsubsection{Jacobi relations}
\ace{I like (and have previously used) the terms \emph{defining} and \emph{boundary} relations for the two types of Jacobi}

@@

\subsubsection{Graph symmetries}

@@

\subsubsection{Unitarity}

>>>>

\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}
Some background here on how we approach color-dual bootstrap (as we will utilize in our two-loop construction). Building an ansatz from irreducible lorentz products (ISPs). Comments about:
\begin{itemize}
\item loop momenta weight counting 
\item polynomial vector spaces 
\item generalized gauge freedom
\item functional jacobi constraints and cuts
\end{itemize}

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
assumptions in searching for double-copyable integrand numerators (ordered accoring to the
reference):
\begin{enumerate}
\item Locality: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
\item Power-counting: The maximum power of the loop momenta in the
  numerator is bounded by Feynman-gauge Feynman rules.
\item Cubic diagrams: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item Relabeling : The diagram numerators are only a function of the
  diagram's topology and labeling.
\item Symmetries: The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}.
\item Unitarity cuts: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\item Color-kinematics duality: The numerators obey some form of the
  kinematic Jacobi relations.
\end{enumerate}
Point 1 is generally a matter of convenience: there are many examples
in which ``numerators'' with controlled rational contributions have
been found \citepls{}.  However, without a guiding principle about
what types of rational terms to use, the size of ans\"{a}tze quickly
get out of hand.  Point 2 was motivated at the time by the hope that
color-dual numerators could arise naturally out of a special gauge
choice.  However, recent work by Ben-Shahar, Garozzo, and Johansson
\cite{Ben-Shahar:2022ixa} \ace{Are there other good examples?}
demonstrates that constructing Feynman rules which produce manifestly
color-dual numerators for the NMHV sector of Yang--Mills requires
introducing additional auxiliary fields, including higher-spin modes,
which could shift the expected power counting in non-trivial ways.
Point 3 is a requirement of the BCJ double-copy: currently there is no
known way of incorporating non-cubic diagrams into the kinematic
Jacobi relations.  Points 4 and 5 will be elaborated on in
\cref{sec:syms}, Point 6 in \cref{sec:unitarity}, and Point 7 in
\cref{sec:jac-rels}.

@@

\subsubsection{Jacobi relations}
\label{sec:jac-rels}
\ace{I like (and have previously used) the terms \emph{defining} and \emph{boundary} relations for the two types of Jacobi}

@@

\subsubsection{Graph symmetries}
\label{sec:syms}

@@

\subsubsection{Unitarity}
\label{sec:unitarity}
